Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion Temperature \\ Gradient-Driven Turbulence

### 2023-06-25 presentation/presentation.tex
#39: Minor corrections and notes for slides
#39: Sheraing rate plot in zonal flow chapter and presentation
#39: Shorter presentation with less theory

	%\begin{frame}{Gliederung}
	%	\tableofcontents[hideallsubsections]
	%\end{frame}

@@

	\begin{frame}
		\frametitle{Zonal Flows}
		\begin{center}
			\onslide<2->\includegraphics[width = 0.8\paperwidth]{Theory/Zonal-Flow-Generation.pdf}
			%\begin{itemize}
			%	\item <3-> Zonal flows are linked to the $\exb$ flows
			%	\item <4-> Zonal flow is tangential to the flux-surfaces and does not contribute to the turbulent transport across the flux-surfaces
			%\end{itemize}
		\end{center}
	\end{frame}

		\onslide<2-> Pattern formation occurs in the stabilized tokamak plasma the so-called $\exb$ staircase structure. \\\bigskip

		\onslide<3-> Properties:
		\begin{enumerate}
			\item[(1)] <4-> \textit{Radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <5-> \textit{Quasi stationary} in space 
			\item[(3)] <6-> Time scales much longer than the typical turbulence time scales
			\item[(4)] <7-> \textit{Typical amplitude} of the order of $10^{-1} \vth/R$.
			\item[(5)] <8-> Turbulent transport strongly linked to the local $\exb$ shearing through \textit{avalanches}
		\end{enumerate}
		\onslide<9->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

	%\begin{frame}
	%	\frametitle{Vlasov Equation}
	%	\begin{gather*}
	%		\frac{\partial f}{\partial t} + \frac{\partial f}{\partial \vect{x}} \cdot \frac{\mathrm{d}\vect{x}}{\mathrm{d}t} + \frac{\partial f}{\partial \vect{v}} \cdot \frac{\mathrm{d}\vect{v}}{\mathrm{d}t} = 0
	%	\end{gather*}
	%	\begin{gather*}
	%		n = \int \mathrm{d}\vect{v}\,f(\vect{x}, \vect{v}, t) \qquad j = q \int \mathrm{d}\vect{v}\, v f(\vect{x}, \vect{v}, t)
	%	\end{gather*}
	%	\begin{gather*}
	%		\begin{aligned}
	%			\nabla \cdot \vect{B} &= 0 &\qquad \nabla \times \vect{B} &= \mu_0\left( \sum_\mathrm{species} j + \epsilon_0 \frac{\partial \vect{E}}{\partial t} \right) \\
	%			\nabla \cdot \vect{E} &= \frac{1}{\epsilon_0} \sum_\mathrm{species} qn &\qquad \nabla \times \vect{E} &= - \frac{\partial \vect{B}}{\partial t}
	%		\end{aligned}
	%	\end{gather*}
	%\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$ (normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$ and $\rhoth = \frac{m \vth}{|q|B}$)) 
				\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <8-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<2-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<2-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <3-> Zonal flow mode that dominates the staircase pattern are called \textbf{basic mode} 
				\item <4-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause

@@

		\begin{center}
		    \begin{tikzpicture}[node distance=1.5cm]

@@

		    \end{tikzpicture}
		\end{center}
	\end{frame}

	\begin{frame}
		\frametitle{Restart Script}

		\begin{center}
		    \begin{tikzpicture}[node distance=2cm]

@@

		    \end{tikzpicture}
		\end{center}

	\begin{frame}
		\frametitle{Restart Script}

		\begin{center}
		    \begin{tikzpicture}[node distance=1.5cm]

@@

		    \end{tikzpicture}
		\end{center}

@@

			\only<9>{\includegraphics[height = 0.7\paperheight]{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/noise/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_noise_wexb_dens_ene_selection.pdf}}

			\only<10>{\textbf{(3) Binormal} \\[0.5cm] $\NR \times \NB \in [3\times1.5,~3\times2.5,~3\times3,~3\times5]$}

			\only<11>{\includegraphics[width = 0.8\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_comparison_thesis.pdf}}

			\only<12>{\includegraphics[height = 0.5\paperheight]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}}

			\only<14>{
				\textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}\bigskip

@@

>>>>

@@

	\begin{frame}
		\frametitle{Zonal Flows \& Shearing Rate}

		\begin{center}
			\only<2>{\includegraphics[width = 0.8\paperwidth]{Theory/Zonal-Flow-Generation.pdf}}

			\only<3>{
				\begin{tabular}{c c}
					\includegraphics[height = 0.75\paperheight]{Theory/Shearing-Rate.pdf} &
					$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$\\
				\end{tabular}
			}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Simulation setup orientates on Paper from Arthur Peeters in the year 2016
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$
				%\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <7-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<2-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<2-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <3-> Zonal flow mode that dominates the staircase pattern are called \textbf{basic mode} 
				\item <4-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
				\item <5-> Waltz criterion $|\wexb|\approx\gamma$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause

@@

		\begin{center}

			\only<2>{
		    \begin{tikzpicture}[node distance=1.5cm]

@@

		    \end{tikzpicture}
			}

			\only<3>{
		    \begin{tikzpicture}[node distance=2cm]

@@

		    \end{tikzpicture}
			}

			\only<4>{
		    \begin{tikzpicture}[node distance=1.5cm]

@@

		    \end{tikzpicture}
			}

		\end{center}

@@

			\only<9>{\textbf{(3) Binormal} \\[0.5cm] $\NR \times \NB \in [3\times1.5,~3\times2.5,~3\times3,~3\times5]$}

			\only<10>{\includegraphics[width = 0.8\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_comparison_thesis.pdf}}

			\only<11>{\includegraphics[height = 0.5\paperheight]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}}

			\only<12>{
				\textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}\bigskip

@@

%--------------------------------------------------------------------------
% Appendix
%--------------------------------------------------------------------------

	\appendix

		\only<10>{
			\begin{center}
				\includegraphics[height = 0.75\paperheight]{Theory/Shearing-Rate.pdf}
			\end{center}
			\bigskip
		}
		\onslide<2-> Pattern formation occurs in the stabilized tokamak plasma the so-called $\exb$ staircase structure. \\\bigskip

		\onslide<3-> Properties:
		\begin{enumerate}
			\item[(1)] <4-> \textit{Radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <5-> \textit{Quasi stationary} in space 
			\item[(3)] <6-> Time scales much longer than the typical turbulence time scales
			\item[(4)] <7-> \textit{Typical amplitude} of the order of $10^{-1} \vth/R$ (Waltz criterion $|\wexb|\approx\gamma$)
			\item[(5)] <8-> Turbulent transport strongly linked to the local $\exb$ shearing through \textit{avalanches}
		\end{enumerate}
		\onslide<9->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

	\begin{frame}
		\frametitle{Size Convergence of $\exb$ Staircase Pattern}
		\begin{center}

			\includegraphics[height = 0.7\paperheight]{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/noise/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_noise_wexb_dens_ene_selection.pdf}

		\end{center}
	\end{frame}
